The benefits of reporting critical effect size values

### 2024-12-16 paper/paper.Rmd
final

keywords          : critical effect size values, statistical significance, hypothesis testing, effect sizes 
wordcount         : "4676"

@@

Beyond critical effect size values, researchers should reason before conducting a study on what conclusions can be drawn with their experimental design, and for those cases where sample size constrains will make it impossible to find significance for a plausible effect because it is likely smaller than the critical effect size value, alternative options for data collection, such as multisite studies [@sirois2023pupil; @moshontz2018psychological; @jarke2022roadmap; @byers2020building], should be explored.

>>>>

keywords          : critical effect size values, statistical significance, hypothesis testing, effect sizes 
wordcount         : "4745"

@@

Beyond critical effect size values, researchers should carefully consider, before conducting a study, what conclusions can realistically be drawn from their experimental design. The more complex the study design, the higher the critical effect size value. Researchers should assess whether their available sample size allows them to address a simpler yet still relevant question. If this is not feasible, and sample size constraints make it impossible to detect significance for a plausible effect because it is smaller than the critical effect size value, alternative data collection strategies, such as multisite studies [@sirois2023pupil; @moshontz2018psychological; @jarke2022roadmap; @byers2020building], should be considered. Lastly, if participating in or leading a multisite study is not an option, researchers should evaluate whether collecting the sample for exploratory analysis without making inferences might still be valuable. Such data could later be included in a meta-analysis.

### 2024-12-16 paper/paper.tex
final

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{critical effect size values, statistical significance, hypothesis testing, effect sizes\newline\indent Word count: 4676}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

@@

Beyond critical effect size values, researchers should reason before conducting a study on what conclusions can be drawn with their experimental design, and for those cases where sample size constrains will make it impossible to find significance for a plausible effect because it is likely smaller than the critical effect size value, alternative options for data collection, such as multisite studies (Byers-Heinlein et al., 2020; Jarke et al., 2022; Moshontz et al., 2018; Sirois et al., 2023), should be explored.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{critical effect size values, statistical significance, hypothesis testing, effect sizes\newline\indent Word count: 4745}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

@@

Beyond critical effect size values, researchers should carefully consider, before conducting a study, what conclusions can realistically be drawn from their experimental design. The more complex the study design, the higher the critical effect size value. Researchers should assess whether their available sample size allows them to address a simpler yet still relevant question. If this is not feasible, and sample size constraints make it impossible to detect significance for a plausible effect because it is smaller than the critical effect size value, alternative data collection strategies, such as multisite studies (Byers-Heinlein et al., 2020; Jarke et al., 2022; Moshontz et al., 2018; Sirois et al., 2023), should be considered. Lastly, if participating in or leading a multisite study is not an option, researchers should evaluate whether collecting the sample for exploratory analysis without making inferences might still be valuable. Such data could later be included in a meta-analysis.
